--- 
title: "BAYESIAN INDEX MODELS FOR HETEROGENEOUS TREATMENT EFFECTS"
date: "<small>`r Sys.Date()`</small>"
output:
  html_document:
    css: Format.css
    toc: yes
    toc_depth: 3
    number_sections: true
    toc_float: 
      collapsed: false
    code_folding: hide
    theme: cerulean
description: "some description ..."
---

```{r setup,echo=FALSE}
require(Hmisc)    # provides knitrSet and other functions
knitrSet(lang='markdown', fig.path='png/', fig.align='left', w=6.5, h=4.5, cache=TRUE)
knitrSet(lang='blogdown')
```



# Simple linear model using brms

If the interaction term is included in the model, the brms package automatically inserts an intercept and the main effect of the treatment (A) into the fitted Bayesian model.

Thus, the simple linear model with the brms package would be:

$$
\begin{aligned} 
logit(P(Y_i=1)) &= \tau + \boldsymbol{X_i}^\top \boldsymbol{m} +(A_i-\bar{A})\beta_0 + (A_i-\bar{A})\boldsymbol{X_i}^\top\boldsymbol{\beta}\\
\tau &\sim Normal(df=3,\mu=0,\sigma=8)\\
\boldsymbol{m} &\sim Normal(\boldsymbol\mu=0,\Sigma=\ 5^2 \boldsymbol{I}_{p\times p})\\
\beta_0 &\sim Normal(\mu=0,\sigma=5)\\ 
 \boldsymbol{\beta} &\sim Normal(\mu=\boldsymbol{0},\Sigma=5^2 \boldsymbol{I}_{p\times p})\\
 \end{aligned}
$$

# Simulation results for all scenarios
```{r}
library("collapse")
library("dplyr")
library("data.table")
library("tidyverse")
library("kableExtra")
library("table1")
load("C:/Users/Danni/OneDrive - NYU Langone Health/Side projects/BayesSIMML/results_testlinearcode/Submit_v2/results/all_24_scenarios_brms.rda")

results <- unlist2d(results.aggregated2, idcols = "replicate",DT = TRUE)#the first columns: scenario's id;the second column:simulation's id for each secnario
pri_scen <- function(x){
  paste0(x["replicate"],". ","n=",x["n"],","," p=",x["p"],","," g.choice=",x["g.choice"],",",
         " m.choice=",x["m.choice"])
}

results$scenario <- apply(results,1,pri_scen)
kable(results, "html") %>% kable_styling("striped") %>% scroll_box(height = "300px")
```
# Summary statistics

- bsim.deviance: deviance from Bayesian single index model (BSIM)

- sng.bayes.deviance: deviance from Bayesian linear model (BLM)

- bsim.accuracy：the proportion of correct decision (PCD) from BSIM

- sng.bayes.accuracy: PCD from BLM

- bsim.value: the expected outcome under the treatment regime using BSIM

- sng.bayes.value: the expected outcome under the treatment regime using BLM

- opt.value: the expected outcome under the treatment regime using true value of parameters in for the data generation

```{r}
#myVars <- c("bsim.deviance","bsim.accuracy","sng.bayes.deviance","sng.bayes.accuracy",
#"bsim.value","sng.bayes.value","opt.value")
#paste(" ",paste(myVars, collapse=" + "), sep=" ~ ")

table1(~ bsim.deviance +  sng.bayes.deviance + 
         bsim.accuracy + sng.bayes.accuracy + bsim.value + 
         sng.bayes.value + opt.value| scenario,data=results,
       overall=FALSE,transpose=TRUE,topclass="Rtable1-zebra")
```


# Deviance

```{r}
m_dev <- results %>% 
  group_by(replicate) %>% 
  dplyr::summarise(mean_dev_bsim=mean(bsim.deviance), mean_dev_sng=mean(sng.bayes.deviance),
                   sd_dev_bsim=sd(bsim.deviance), sd_dev_sng=sd(sng.bayes.deviance)) 

l_dev <- reshape2::melt(m_dev,id=c("replicate"))
sd <- l_dev %>% subset(variable %in% c("sd_dev_sng","sd_dev_bsim"))
colnames(sd) <- c("replicate","variable_sd","value_sd")
mean_dev <- l_dev %>% subset(variable %in% c("mean_dev_bsim","mean_dev_sng"))
plot_dev <- cbind(mean_dev,sd[,-1])

plot_dev$replicate <- as.factor(plot_dev$replicate)

ggplot(plot_dev, aes(x=replicate, y=value, color=variable)) + 
  geom_point()+
  geom_errorbar(aes(ymin=value - value_sd, ymax=value + value_sd), width=.2,
                position=position_dodge())+ 
  labs(title="Mean (+- standard deviation) of deviance based on 100 simulations",
        y = "Deviance", x= "Scenario")+ theme(legend.position="bottom")+
  scale_color_discrete(name = "Model", labels = c("BSIM", "BLM"))

```

```{r}
dev <- results[,c("replicate","bsim.deviance","sng.bayes.deviance")]

dev <- reshape2::melt(dev,id=c("replicate"))
dev$replicate <- as.factor(dev$replicate)
ggplot(dev, aes(x=replicate, y=value,fill=variable)) +
  geom_boxplot(outlier.size=0.5)+ 
  labs(title="Boxplot of deviance based on 100 simulations",
        y = "Deviance", x= "Scenario")+ theme(legend.position="bottom")+
  scale_fill_discrete(name = "Model", labels = c("BSIM", "BLM"))
```

# The expected outcome under the treatment regime

Different from  the stan model(in iImulation_BSIMML_stan.html), the optimal treatment decision rule depends on the contrast:$\Delta = \beta_0+\boldsymbol{X_i}^\top\boldsymbol{\beta}$. 

```{r}
m_e_y <- results %>% 
  group_by(replicate) %>% 
  dplyr::summarise(mean_y_bsim=mean(bsim.value), mean_y_sng=mean(sng.bayes.value),
                   mean_y_optim = mean(opt.value),
                   sd_y_bsim=sd(bsim.value), sd_y_sng=sd(sng.bayes.value),
                  sd_y_optim = sd(opt.value), ) 

l_y <- reshape2::melt(m_e_y,id=c("replicate"))
sd <- l_y %>% subset(variable %in% c("sd_y_sng","sd_y_bsim","sd_y_optim"))
colnames(sd) <- c("replicate","variable_sd","value_sd")
mean_y <- l_y %>% subset(variable %in% c("mean_y_bsim","mean_y_sng","mean_y_optim"))
plot_y <- cbind(mean_y,sd[,-1])

plot_y$replicate <- as.factor(plot_y$replicate)

ggplot(plot_y, aes(x=replicate, y=value, color=variable)) + 
  geom_point()+
  geom_errorbar(aes(ymin=value - value_sd, ymax=value + value_sd), width=.2,
                position=position_dodge())+ 
  labs(title="Mean (+- SD) of the expected outcome under the treatment regime",
        y = "The expected outcome under the treatment regime", x= "Scenario")+ theme(legend.position="bottom")+
  scale_color_discrete(name = "Model", labels = c("BSIM", "BLM","True optimal value using true value of parameters"))

```

```{r}
e_y <- results[,c("replicate","bsim.value","sng.bayes.value","opt.value")]

e_y <- reshape2::melt(e_y,id=c("replicate"))
e_y$replicate <- as.factor(e_y$replicate)
ggplot(e_y, aes(x=replicate, y=value,fill=variable)) +
  geom_boxplot(outlier.size=0.5)+ 
  labs(title="Boxplot of the expected outcome under the treatment regime",
        y = "The expected outcome under the treatment regime", x= "Scenario")+ theme(legend.position="bottom")+
  scale_fill_discrete(name = "Model", labels = c("BSIM", "BLM","True optimal value using true value of parameters"))
```


# PCD

```{r}
m_pcd <- results %>% 
  group_by(replicate) %>% 
  dplyr::summarise(mean_pcd_bsim=mean(bsim.accuracy), mean_pcd_sng=mean(sng.bayes.accuracy),
                   sd_pcd_bsim=sd(bsim.accuracy), sd_pcd_sng=sd(sng.bayes.accuracy)) 

l_pcd <- reshape2::melt(m_pcd,id=c("replicate"))
sd <- l_pcd %>% subset(variable %in% c("sd_pcd_sng","sd_pcd_bsim"))
colnames(sd) <- c("replicate","variable_sd","value_sd")
mean_pcd <- l_pcd %>% subset(variable %in% c("mean_pcd_bsim","mean_pcd_sng"))
plot_pcd <- cbind(mean_pcd,sd[,-1])

plot_pcd$replicate <- as.factor(plot_pcd$replicate)

ggplot(plot_pcd, aes(x=replicate, y=value, color=variable)) + 
  geom_point()+
  geom_errorbar(aes(ymin=value - value_sd, ymax=value + value_sd), width=.2,
                position=position_dodge())+ 
  labs(title="Mean (+- SD) of PCD based on 100 simulations",
        y = "PCD", x= "Scenario")+ theme(legend.position="bottom")+
  scale_color_discrete(name = "Model", labels = c("BSIM", "BLM"))

```

```{r}
pcd <- results[,c("replicate","bsim.accuracy","sng.bayes.accuracy")]

pcd <- reshape2::melt(pcd,id=c("replicate"))
pcd$replicate <- as.factor(pcd$replicate)
ggplot(pcd, aes(x=replicate, y=value,fill=variable)) +
  geom_boxplot(outlier.size=0.5)+ 
  labs(title="Boxplot of PCD based on 100 simulations",
        y = "PCD", x= "Scenario")+ theme(legend.position="bottom")+
  scale_fill_discrete(name = "Model", labels = c("BSIM", "BLM"))
```